Aligning species range data to better serve science and conservation

### 2016-01-14 ms_6_supplemental.Rmd
updating SOM

### illustrative maps for different quadrants and different mechanistic problems

### descriptions of IUCN and AM data sets

@@

__Add'l maps to show mechanistic causes of quadrants__

>>>>

## Info on data prep

### processing AquaMaps

* start with .sql files - three of 'em - how to get 'em?
* turn into .csvs, which columns are critical for this analysis? simplify

### downloading and processing IUCN maps

* which data sets are included?
* raster::extract() to convert polys to csvs
* which columns are included?

### creating master species list for co-listed species

* using AquaMaps and IUCN, and IUCN master list, create the big list
* which columns are included?
* adjust this master list to use IUCN SID only for parent - eliminate the whole question of parent/subpop? for the purpose of this analysis

## descriptions of IUCN and AM data sets

@@

## illustrative maps for different quadrants and different mechanistic problems

a few codes to indicate likely problems?

- DC = depth clipping; IUCN extents go beyond reasonable depth for the species
- DX = data excluded; AM excludes some observations that appear to be used for IUCN
- DP = data poor (AquaMaps acknowledges data poor status? or use less than 10 data points as criteria)
- NX = needs evaluation by expert; AM model likely predicts areas where species is unlikely to be found based on observed occurrences - does AM model reflect same as AM suitable habitat?

Q2:

| species                | quad | group           | codes   | notes |
| -------                | ---- | -----           | -----   | ----- |
| Conus episcopatus      | q2   | cones           |  DP, DX | d-match around Coral Triangle, but IUCN shows much more around Indian Ocean and S Pacific; also IUCN extents
| Ctenochaetus binotatus | q2   |                 |         | IUCN extents beyond AM
| Naso vlamingii         | q2   | acanthuridae    |         | IUCN extents beyond AM
| Thalassoma purpureum   | q2   | wrasses         |         | IUCN extents beyond AM
| Porites nigrescens     | q2   | corals 2        | DP      | AM limited to CT; IUCN shows far greater dist, and extents
| Conus ammiralis        | q2   | cones           | DP      | AM  | limited to CT, IUCN shows in Madagascar; also extents
| Conus tessulatus       | q2   | cones           |         | extents
| Acropora sarmentosa    | q2   | corals 1        |         | extents; also AM shows HI but IUCN does not?
| Holothuria fuscogilva  | q2   | sea cucumbers   |         | extents; also AM shows Mex and Central Am west coast, but IUCN does not (not available online?)
| Oculina Varicosa       | q2   | corals 2        |         | lim to Caribbean; extents - this might be a good close-up map
| Acanthocybium solandri | q2   | tunas/billfish  |         | mostly tropical by IUCN; AM shows much farther N and S

Q3

| species                | quad | group           | codes   | notes |
| -------                | ---- | -----           | -----   | ----- |
| Conus magnificus       | q3   |  cones          |         | IUCN distribution is more limited than AM distribution)
| Abudefduf concolor     | q3   |  damselfish     |         | Baja for AM, southern Central Am for IUCN; maybe a good closeup map?  AM points from Baja to Peru incl Galapagos; some rejected pts from Caribbean and eastern Atlantic
| Centropyge aurantonotus | q3  |  angelfish      |         | AM shows Caribbean; IUCN shows northern South America, also maybe a good closeup map? AM points from FL to south Brazil, but no Gulf of Mexico.
| Chlorurus perspicillatus | q3 |  parrotfish     |         | IUCN shows only HI; AM shows dots all over S Pacific and near Marianas Islands
| Sarda orientalis        | q3  |  tunas/billfish |         | limited dists by IUCN
| Montastraea franksi     | q3  |  corals 2       | DP      | IUCN shows just in Caribbean; AM shows all up & down east coast of N America and S America

Q4

| species                  | quad | group   | codes   | notes |
| -------                  | ---- | -----   | -----   | ----- |
| Acanthurus nigroris      | q4   |         |         | IUCN dist limited to HI, while AM shows all over S Pacific and CT - AM observations all over S pacific...
| Praealticus tanegasimae  | q4   | blenny  |         | IUCN shows limited dist around Japan/Marianas; AM shows much broader through CT and W Pacific - good local map?
| Stethojulis marquesensis | q4   | wrasse  |         | IUCN shows only small cluster of islands (Marquesas?) while AM shows much broader across S Pacific
| Canthigaster leoparda    | q4   | puffer  |         | IUCN limited spots around a couple of islands; AM shows all throughout CT
| pentacheles snyderi      | q4   | lobster | DP      | AM shows all over - sim to depth profiles? while IUCN shows only a couple patches - HI? S Pacific, and S Indian oceans?  AM limits to specific FAO regions, which results in odd cutoffs; also shows some data points in N Atlantic which has an odd result.
| Nephropsis sulcata       | q4   | lobster |         | IUCN shows odd ranges, most of which don't overlap with AM
